---
output:
  html_document:
    keep_md: yes
    theme: cerulean
---
```{r CountFeatures,echo=FALSE,results='hide'}
source("run_analysis.R")
averages<-read.table("averages.txt")
```

Code Book
=========

This code book lists all variables (columns) of the results of the analysis 
described in the README.md file. For a detailed description the reader is
refered to the README.txt and features_info.txt files of the orginal researchers
(these are included in the submission).

The data set is located in the *averages.txt* file which contains
`r nrow(averages)` rows of `r ncol(averages)` columns. the columns correspond
to variables while the rows are observations. The data in the table are the averages
of the oroginal retained variables by the activity type and subject.

The first 12 rows and first five columns look like this:

```{r,echo=FALSE,results='asis'}
knitr::kable(averages[1:12,1:5])
```

So for example, in this extract the value **`r averages[1,3]`** is the average of the variable **`r colnames(averages)[3]`** for the activity **`r averages[1,1]`**
for subject **#`r averages[1,2]`**.

The first two columns are

Column | Variable | Description
- | - | -
1        | Activity      | The desciptive name of the activity being performed.
2        | Subject       | THe number of the subject performing the activity.

The subsequent columns are

```{r,echo=FALSE,results='asis'}
cols<-3:ncol(averages)
knitr::kable(data.frame(Column=cols,Variable=colnames(averages)[cols]),align=c('l','l'))
```


